\documentclass[a4paper, 10pt]{article}
% \documentclass[letterpaper, 10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex, hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome}
\usepackage{multicol}

\usepackage[charter]{mathdesign} % Bitstream Charter
% \usepackage{newpxtext,newpxmath} % Palatino

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.50in}
\addtolength{\evensidemargin}{-0.50in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
\vspace{-6pt}\scshape\raggedright\large
}{}{0em}{}[\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{\item\small{\textbf{#1}{: #2}}}

\newcommand{\resumeItemNoSub}[1]{\item\small{{#1}}}

\newcommand{\resumeItemNoBullet}[2]{\item[]\small{\hspace{-9pt}{#1}{: #2}}}

\newcommand{\resumeSubheading}[4]{
\vspace{4pt}\item[]
\begin{tabular*}{0.98\textwidth}{l@{\extracolsep{\fill}}r}
    \hspace{-10pt}\textbf{#1}       & #2                 \\
    \hspace{-10pt}\textit{\small#3} & \textit{\small #4} \\
\end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

% custom commands
\newcommand{\shorterSection}[1]{\vspace{-5pt}\section{#1}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------
\begin{center}
  \textbf{\huge Ramesh Kumar} \\
  \vspace{2pt}
  Software Developer with 7+ Years of experience\\
  \vspace{2pt}
  \href{https:\\linkedin.com/in/rameskum}{\small \faLinkedin \hspace{2pt} in/rameskum}
  $\vert$
  \href{https:\\rameskum.com}{\small \faChain \hspace{1pt} rameskum.com}
  $\vert$
  \href{mailto:rameskum.corp@outlook.com}{\small \faEnvelope \hspace{2pt} rameskum.corp@outlook.com}
  $\vert$
  \faPhone \hspace{1pt} \small{ +1-(437) 518-7719}
  $\vert$
  \small \faMapMarker \hspace{2pt} \small{Toronto, Canada}\\
  % \\
\end{center}

\small
%-----------SUMMARY-----------------
\section{Professional Summary}
% Highly skilled and results-oriented Software Developer with 7+ years of experience designing, developing, and maintaining robust backend systems. Proven expertise in Java, Spring Boot, and API design. Passionate about building scalable and secure applications.

% Experienced Software developer with 7+ years of experience. Passionate about building secure, scalable backend systems with Spring Boot and API design. Proven track record of delivering high-quality solutions.

% Enthusiastic Software Developer with 7 years of experience crafting secure, scalable backend systems using Spring Boot and Java. Adept at API design and delivering high-quality solutions that meet business needs. Driven to continuously improve and expand expertise in cloud deployments and distributed systems.

Detail-oriented Java Developer with over 7 years of experience in developing high-quality, secure and scalable backend systems. Adept at API design and delivering high-quality solutions that meet business needs.

% Java Backend Architect with 7+ years of experience crafting secure, scalable backend systems using Spring Boot and API design. Proven ability to deliver high-quality solutions that drive business impact. (This option positions you as a leader and highlights the impact of your work)

% \resumeSubHeadingListStart
%     \resumeItemNoSub{Technically advanced developer with experience in delivering customer-centric software applications using Java and Spring Boot.}
%     \resumeItemNoSub{Offering strong expertise in JAVA, Restful API design, SQL, Spring, Spring Boot, Micro-services, Docker, SOAP, and JSON.}
%     \resumeItemNoSub{
%     Detail-oriented professional recognized for effective critical thinking, strong debugging, troubleshooting, and problem-solving skills.
%     }
% \resumeSubHeadingListEnd

%-----------SKILLS-----------------
\section{Skills}
\vspace{-10pt}
\begin{multicols}{3}
  \resumeSubHeadingListStart
  
  \item{Java}
  \item{SQL, Postgres, Oracle, MySQL}
  \item{Maven}
  \item{Agile, Scrum, Unit Testing (JUnit)}
  \item{OAuth, OpenID, SAML, JWT}

  \item{Spring Boot, Spring Data}
  \item{Spring MVC, Spring Security}
  \item{Micro Services}
  \item{Docker}
  \item{Next.js}

  \item{Rest API, SOAP, Swagger}
  \item{Git, Perforce}
  \item{SOAP, Rest API, Swagger, JSON, XML}
  \item{OOPs}
  \item{Angular}
  
  \resumeSubHeadingListEnd
\end{multicols}

%-----------EMPLOYMENT-----------------
\section{Work Experience}
\resumeSubHeadingListStart

\resumeSubheading{Amdocs Canada (Zenith SS)}{Jan 2022 - Mar 2024}{Software Developer}{Toronto, Canada}

% \resumeItemListStart
\resumeItemNoSub{Engineered a rollback-enabled tool using NextJS to streamline updating compressed and serialized CLOB database columns, reducing manual effort by 60\% and enhancing operational efficiency. Implemented JWT token-based authentication and authorization for secure access.}
\resumeItemNoSub{Enhanced charge loading efficiency by developing a robust system for bulk charges and tax handling, resulting in a 40\% reduction in billing processing time and enabling seamless operational workflows.}
\resumeItemNoSub{Enhanced the data pipeline to publish and subscribe debit and tax information to and from Google Pub/Sub topic, leveraging Java's concurrent programming capabilities to maximize efficiency and scalability.}
% \resumeItemListEnd

\resumeSubheading{Avaya (BETSOL)}{Sep 2021 -  Jan 2022}{Senior Applications Engineer}{Pune, India}

% \resumeItemListStart
\resumeItemNoSub{Directed the design and rollout of Contract Portal to centralize budget, contract details, expiration dates, and product coverage information. The portal enables support analysts to validate contract terms, accelerating user request resolutions by 5\%.}
\resumeItemNoSub{Formulated and executed a collaborative solution-driven initiative with teams to address and rectify IVR application issues.}
% \resumeItemListEnd


\resumeSubheading {Oracle India Private Limited, IDC}{Mar 2021 - Sep 2021}{Senior Applications Engineer}{Hyderabad, India}

% \resumeItemListStart
\resumeItemNoSub{Directed the creation and execution of a high-volume transaction reconciliation process at Oracle, automating bulk reconciliation tasks, leading to a 50\% reduction in manual effort for end-users.}
\resumeItemNoSub{Collaborated with cross-functional teams to diagnose and address SQL performance challenges impacting applications, reporting systems, and dashboards.}
% \resumeItemListEnd

\resumeSubheading {Amdocs Development Centre India LLP}{Aug 2016 - Feb 2021}{Software Developer}{Pune, India}

% \resumeItemListStart
\resumeItemNoSub{Developed Spring Boot-based Automatic Recovery Tool (ART) to identify and address data inconsistencies. ART generates actionable reports and executes remediation actions, resulting in a 25\% reduction in operational overhead through improved data accuracy and efficiency.}
\resumeItemNoSub{Implemented secure and efficient RESTful APIs to facilitate communication between backend and frontend applications.}
% \resumeItemListEnd

\resumeSubHeadingListEnd

%----------- Personal Projects -----------------
\section{Personal Projects}
\resumeSubHeadingListStart

\resumeItem{HomeLab Server}{Designed and built home lab server featuring Proxmox, Docker, NAS, media server, and secure web access with Nginx. This self-hosted ecosystem facilitates efficient development, hosting and personal project management \href{https://dashboard.computerbyte.in/}{\faChain \hspace{1pt}(Demo)}.}

\resumeItem{Personal Portfolio}{Created an interactive personal portfolio website showcasing proficiency in React, HTML, CSS, JavaScript, and Node.js \href{https:\\rameskum.com}{\faChain \hspace{1pt}(Demo)}.}

\resumeItem{HelloDog - Discover the World of Dog Breeds}{Created a user-centric web application to exhibit diverse dog breeds; employed vanilla JavaScript, HTML, and CSS to fetch data from a REST API and showcase it in an aesthetically pleasing grid layout \href{https://rameskum.github.io/hello-dog/}{\faChain \hspace{1pt}(Demo)}.}

\resumeSubHeadingListEnd

% %-----------Recognition-----------------
% \section{Recognition}

% \resumeSubHeadingListStart
% \resumeItemNoSub{Awarded \textit{backbone of the Operation} title in \textbf{Aug 2020}}
% \resumeItemNoSub{Recognized for category \textit{Make the Complex Simple} in \textbf{October 2018}}
% \resumeItemNoSub{Recognized for \textit{significant contribution to the Telstra and OSS Unit} in \textbf{July 2018}}
% \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading{Master of Technology in Computer Science}{Jun 2014 - Jun 2016}{National Institute of Technology}{Rourkela, India}
% \resumeItemNoBullet{Relevant Coursework}{Vehicular ad-hoc Network, Intelligent Transportation System, Cryptography}

\resumeSubheading{Bachelor of Technology in Computer Science \& Engineering}{Sep 2009 - Jun 2013}{Uttar Pradesh Technical University}{Lucknow, India}
% \resumeItemNoBullet{Relevant Coursework}{Analysis \& Design of Algorithms, Data Structures using C, Operating Systems, Database}

\resumeSubHeadingListEnd
\end{document}